### 2023-02-06 ART_Dodig-Crnkovic/Dodig-Crnkovic.tex
Final commit before sending to the editors for corrections

\begin{artengenv}{Gordana Dodig-Crnkovic}
	{In search of a~common, information-processing, agency-based framework for anthropogenic, biogenic, and abiotic cognition and intelligence}
	{In search of a~common, information-processing, agency-based\ldots}
	{In search of a~common, information-processing, agency-based\\framework for anthropogenic, biogenic, and abiotic cognition\\and intelligence}
	{Chalmers University of Technology,\\University of Gothenburg\\and Mälardalen University, Sweden}
	{Learning from contemporary natural, formal, and social sciences, especially from current biology, as well as from humanities, particularly contemporary philosophy of nature, requires updates of our old definitions of cognition and intelligence. The result of current insights into basal cognition of single cells and evolution of multicellular cognitive systems within the framework of extended evolutionary synthesis (EES) helps us better to understand mechanisms of cognition and intelligence as they appear in nature. New understanding of information and processes of physical (morphological) computation contribute to novel possibilities that can be used to inspire the development of abiotic cognitive systems (cognitive robotics), cognitive computing and artificial intelligence.
	}
	{information, computation, cognition, intelligence, extended evolutionary synthesis, anthropogenic, biogenic and abiotic cognition.}

\section*{Information, computation, cognition, intelligence, and evolution of living organisms}
The notion of information is used nowadays not only to refer to means of communication between humans, but also to denote data structures utilized for communication by other living organisms, even the simplest ones like single cells as used in the fields of bioinformatics or neuroinformatics.

@@

\end{artengenv}

>>>>

\begin{artengenv}{Gordana Dodig-Crnkovic}
	{\label{gordana_start}In search of a~common, information-processing, agency-based framework for anthropogenic, biogenic, and abiotic cognition and intelligence}
	{In search of a~common, information-processing, agency-based\ldots}
	{In search of a~common, information-processing, agency-based\\framework for anthropogenic, biogenic, and abiotic cognition\\and intelligence}
	{Chalmers University of Technology,\\University of Gothenburg\\and Mälardalen University, Sweden}
	{Learning from contemporary natural, formal, and social sciences, especially from current biology, as well as from humanities, particularly contemporary philosophy of nature, requires updates of our old definitions of cognition and intelligence. The result of current insights into basal cognition of single cells and evolution of multicellular cognitive systems within the framework of extended evolutionary synthesis (EES) helps us better to understand mechanisms of cognition and intelligence as they appear in nature. New understanding of information and processes of physical (morphological) computation contribute to novel possibilities that can be used to inspire the development of abiotic cognitive systems (cognitive robotics), cognitive computing and artificial intelligence.
	}
	{information, computation, cognition, intelligence, extended evolutionary synthesis, anthropogenic, biogenic and abiotic cognition.}

\section*{Information, computation, cognition, intelligence, and evolution of living organisms}
\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{T}{}he notion of information is used nowadays not only to refer to means of communication between humans, but also to denote data structures utilized for communication by other living organisms, even the simplest ones like single cells as used in the fields of bioinformatics or neuroinformatics.

@@

\end{artengenv}
\label{gordana_stop}
